\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-18 chapters/1_intro.tex
Start finalizing result section

By applying this method both to 2D urban scenes from the CityScapes dataset and the challenging neuron-segmentation task of 3D EM image stacks, \UPDATE{we show how one of the less-known algorithms included in our framework consistently outperformed all other previously proposed signed graph clustering methods and achieved comparable/superior scores to other complex multi-step pipelines...}
% Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods. Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances. Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes. 
% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
% Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting \UPDATE{pixel features} and then grouping pixels into object instances. In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance. Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances superior and comparable, respectively, to proposal-based methods.
% In this approach, the output of the CNN can be represented as a weighted grid graph such that each node represents a pixel of the image and the weights of the edges define interactions between the pixels. A graph clustering algorithm is then applied to cluster pixels into instances. 
% Finally, the algorithms included in the framework are evaluated on an instance segmentation task, both on 3D biological image stacks (Sec. \ref{sec:neuro_segm_exp}) and 2D urban scenes (Sec. \ref{sec:cityscapes_exp}). Our analysis highlights strengths and weaknesses of each algorithm by comparing their robustness to noise, efficiency and inclination to output a well balanced graph partitioning.

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
\caption{
 (\textbf{a}) Iterations of three different algorithms in the generalized framework on  toy graph examples with attractive (green) and repulsive (red) interactions. (\textbf{b}) Example of CREMI 2016 neuron-segmentation data \cite{cremiChallenge} overlaid with instance segmentation. (\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

By applying this method both to 2D urban scenes from the CityScapes dataset and the challenging neuron-segmentation task of 3D EM image stacks, \UPDATE{we show how one of the less-known algorithms included in our framework consistently outperformed all other previously proposed signed graph clustering methods and achieved comparable/superior scores to other complex multi-step pipelines...}

Contributions: generalized framework given by simple algorithm; proof of equivalence with previously proposed methods; new algorithms included; on instance image segmentation, one of the less-known methods in our methods achieved remarkable scores compared to previously aggl. methods proposed; comparable scores to much more complex multi-step pipelines; extensive set of experiments with noise, highlighting the properties of different agglomerative methods; over-clustering and under-clustering

% Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods. Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances. Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes. 
% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
% Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting \UPDATE{pixel features} and then grouping pixels into object instances. In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance. Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances superior and comparable, respectively, to proposal-based methods.
% In this approach, the output of the CNN can be represented as a weighted grid graph such that each node represents a pixel of the image and the weights of the edges define interactions between the pixels. A graph clustering algorithm is then applied to cluster pixels into instances. 
% Finally, the algorithms included in the framework are evaluated on an instance segmentation task, both on 3D biological image stacks (Sec. \ref{sec:neuro_segm_exp}) and 2D urban scenes (Sec. \ref{sec:cityscapes_exp}). Our analysis highlights strengths and weaknesses of each algorithm by comparing their robustness to noise, efficiency and inclination to output a well balanced graph partitioning.

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
\caption{
 (\textbf{a}) Iterations of three different algorithms in the generalized framework on  toy graph examples with attractive (green) and repulsive (red) interactions. (\textbf{b}) Example of CREMI 2016 neuron-segmentation data \cite{cremiChallenge} overlaid with instance segmentation. (\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
 \TODO{show nice segmentations, affinities and replace unsigned case}
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

### 2019-05-18 chapters/2_rel_work.tex
Start finalizing result section

\section{Related work} \label{sec:related_work}
% In recent years there has been considerable progress in pixel-level understanding tasks of computer vision, such as semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
Recent progress in semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
and pose estimation \cite{wei2016convolutional,cao2017realtime} was mostly associated with new key ideas and architectures in deep learning, like dilated convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.

\textbf{Proposal-based methods} decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}. 
% Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring
% \item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.

>>>>

\section{Related work} \label{sec:related_work}
% Recent progress in semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
% and pose estimation \cite{wei2016convolutional,cao2017realtime} was mostly associated with new key ideas and architectures in deep learning, like dilated convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.
\textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}. They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}. 
% Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring
% \item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.

### 2019-05-18 chapters/3_algorithm.tex
Update impl. and complexity section
Add comparison details to suppl.
Start finalizing result section

\textbf{Multicut and correlation clustering } For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
\begin{equation}
E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
\end{equation}
% \begin{align}
% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
% E^1_\Pi &= E \setminus E^0_\Pi.
% \end{align}
The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t. clustering $\Pi$. The instance of the NP-hard \emph{weighted correlation clustering/multicut problem} 
% w.r.t. $\mathcal{G}(V,E,\cost)$ 
corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
\begin{equation}\label{eq:multicut_obj}
% \min_\Pi \texttt{MC}(\Pi) \equiv
 \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
 \begin{cases} 
 1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
 0 & \text{otherwise}.
 \end{cases}
\end{equation}
In the next chapters we will use this objective as measure of how balanced a clustering is.

@@

The proposed \algname{} Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters. It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

@@

In the Supplementary material we comment on the algorithm \UPDATE{computational complexity $\mathcal{O}(?)$} and present an efficient implementation based on an edge contraction algorithm combined with a priority queue (Sec. \ref{sec:complexity}).

@@

\begin{table*}
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{c r  l ?? c | c | c}
            % \toprule\toprule
            \multicolumn{3}{c??}{}  & \multirow{2}{*}[-0.5em]{\textbf{Unsigned Graphs}} & \multicolumn{2}{c}{\textbf{Signed Graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
            \multicolumn{3}{c??}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\

            % \midrule[0.15em]
            \cmidrule[0.15em]{2-6}\morecmidrules \cmidrule[0.15em]{2-6}
            % \midrule \midrule
            \multirow{5}{*}[-1.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ 
            \cmidrule[0.07em]{2-6}

             &\makecell[r]{Absolute \\Max:} & 
            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
               & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\
              \cmidrule[0.07em]{2-6}
             & \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ 
            \cmidrule[0.07em]{2-6}
           % \midrule

            & Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ 
            \cmidrule[0.07em]{2-6}

            & Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}

>>>>

@@

\TODO{mention detailed pseudocode} The proposed \algname{} Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters. It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

@@

In Appendix \ref{sec:detailed_impl} we comment on the algorithm \UPDATE{computational complexity $\mathcal{O}(N^2 \log N)$} and present an efficient implementation based on an edge contraction algorithm combined with a priority queue.

@@

\begin{table*}
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{c r  l ? c | c | c}
            % \toprule\toprule
            \multicolumn{3}{c?}{\multirow{2}{*}[-0.5em]{\thead{\textbf{}}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
            \multicolumn{3}{c?}{} &  &  \multicolumn{1}{c|}{\thead{No Constraints}} & \thead{With Constraints} \\

            \midrule[0.3em]
            % \cmidrule[0.3em]{2-6}
            % \morecmidrules \cmidrule[0.15em]{2-6}
            % \midrule \midrule
            \multirow{5}{*}[-0.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ 
            % \cmidrule[0.07em]{2-6}

             &\makecell[r]{Absolute Max:} & 
            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
               & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\
              % \cmidrule[0.07em]{2-6}
             & \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\ 
            % \cmidrule[0.07em]{2-6}
           % \midrule

            & Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\ 
            % \cmidrule[0.07em]{2-6}

            & Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}

### 2019-05-18 chapters/5_experiments_cityscapes.tex
Start finalizing result section

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. For our experiments, we used the state-of-the-art proposal-free pipeline proposed in \cite{liu2018affinity} (GMIS) that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
Their trained model was publicly available, so we simply replaced their final graph-merging algorithm (GMIS-Agglo) with \algname{}. See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.

Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. GMIS-Agglo requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
For our experiments, we used the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}. See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.

Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. \UPDATE{In Appendix, Table \ref{tab:extended_results_cityscapes} includes all other tested linkage}. MultiStepHAC requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

### 2019-05-18 chapters/5_experiments_compare_rules.tex
Add more details about CS exps
Start finalizing result section

\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Arand-Scores on CREMI challenge training data}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|c|c}
         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
PNI-UNet & 0.228 & 0.116 \\
Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
    \captionof{table}{\UPDATE{TBD:} Scores on test data}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}

\subsection{CREMI Challenge} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score\cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for all details on this and the following methods). On the other hand, almost all state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, as we showed in the related work section. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a distance transform generated from a boundary map (WSDT). In our comparison we use approximated methods of the multicut (MC) and lifted multicut problem (LMC).

>>>>

\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
DTWS + \algname{} & Average& \TODO{} \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Arand-Scores achieved by Different post-processing methods on CREMI challenge training predictions}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|c|c}
         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
PNI-UNet & 0.228 & 0.116 \\
Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
    \captionof{table}{Current leaderboard of the CREMI challenge \TODO{Update refs}}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}

\subsection{CREMI Challenge} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods). On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). The algorithms employed in our comparison to partition the superpixel graph were given by \TODO{\algname{}} (WSDT+\algname{}) or approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.
